Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-09-30 forecast/paper/response-to-reviewers.tex

\begin{resp}
  We have tried to focus mainly on simple time series models in this paper
  rather than comparing to other more elaborate models. A careful
  (out-of-sample) comparison of forecasting performance for state-of-the-art
  models can be found in reference 6 (Cramer et al.). That paper focuses on
  forecasting deaths rather than cases and at the state-level rather than
  disaggregated HRRs. However, their ranking (Figure 2 of Cramer et al.) puts the
  ``COVIDhub-Baseline'' about 10th out of 27 models. As we discuss in the
  manuscript, that baseline is  
  the
  same as the baseline we use for forecasting in this paper: it propagates today
  forward and resamples the residuals to create quantiles (we have expanded the
  description on page 6 to be more explicit). All our ``simplistic'' models beat
  this baseline (the AR(3) does as well). For comparison, IHME (along with 17 other
  ``state-of-the-art'' models) does not. We would argue that using any of the
  models in this paper would be preferable to relying on many of the
  ``widely-used'' models if the goal is forecast accuracy.

  $\bullet$ We have added a sentence to the introduction (around line 40) that
  describes the performance of simple models relative to widely-used models as
  shown in Cramer et al.

  $\bullet$ We have expanded our description of our baseline model (around line
  457). In particular, we emphasize that it is the same as that used by the
  COVID-19 Forecast Hub.

  $\bullet$ We have added two figures to the supplement along with a section of
  text (Section 9) that compares our forecasts with state-of-the-art forecasts
  submitted to the COVID-19 Forecast Hub. The first (Figure S26) overlays the
  scores from the submissions on top of Figure 3 from the manuscript. We should
  note that the submitted forecasts are at the state level, while ours are at
  the HRR level, but once scaled by the baseline, should be roughly comparable.
  Only those forecasters that submitted at least 300 forecasts (roughly 50
  states over 6 weeks during the 6 months examined) are shown. From this Figure
  it is clear that all of the forecasters considered in this paper beat most
  submissions. 
\end{resp}

### 2021-09-30 forecast/paper/paper.tex
modifications after the first revision meeting.

While forecasting carries a rich literature that offers a wide range of
techniques, see e.g., \cite{Hyndman:2018}, we purposely constrain ourselves to
very simple models, avoiding common enhancements such as order selection,
correction of outliers/anomalies in the data, and inclusion of regularization or
nonlinearities.
% Addition in response to Reviewer 1
For the same reason, we do not account for any environmental factors that may
well aid in forecasting---age structure, variants, holidays,
reporting patterns, vaccination, public health measures, etc.
% End addition
That said, analyses of forecasts submitted to the COVID-19
Forecast Hub \cite{ForecastHub} by a large community of modelers have shown that
simple, robust models have consistently been among the best-performing over the
pandemic, including time series models similar to those we
consider in what follows.
% Added in response to Reviewer 2
\cite{Cramer:2021} investigates the performance of submitted forecasts for
state-level deaths and shows that time series models perform among the top 5.
Our internal evaluations suggest that the same is true (at least, if not to a
greater extent) for case forecasting.

@@

Finally, it is worth noting that examining the importance of additional features
for prediction is a core question in inferential statistics and econometrics,
with work dating back to at least \cite{Granger:1969}. Still today, drawing
rigorous inference based on predictions, without (or with lean) assumptions, is
an active field of research from both the applied and theoretical angles;
see, e.g., \cite{Diebold:2002, McCraken:2007, Diebold:2015, Stokes:2017,
  Lei:2018, Rinaldo:2019, Williamsom:2020, Zhang:2020, Dai:2021, Fryer:2021}.
Our take on this problem is in line with much of this literature; however, in
order to avoid making any explicit assumptions, we do not attempt to make formal 
significance statements, and instead, broadly examine the stability of our
conclusions with respect to numerous modes of analysis.
% Addition upon review
We have included a section in the Supplement that examines two assumption-lean
methods for assessing the statistical significance of our main results.

>>>>

While forecasting carries a rich literature that offers a wide range of
techniques, see e.g., \cite{Hyndman:2018}, we purposely constrain ourselves to
very simple models, avoiding common enhancements such as order selection,
correction of outliers/anomalies in the data, and inclusion of regularization or
nonlinearities.
% Addition in response to Reviewer 1
For the same reason, we do not account for any environmental factors that may
well aid in forecasting---age structure, variants, holidays,
reporting patterns, vaccination, public health measures, etc.
% End addition
That said, analyses of forecasts submitted to the COVID-19
Forecast Hub \cite{ForecastHub} by a large community of modelers have shown that
simple, robust models have consistently been among the best-performing over the
pandemic, including time series models similar to those we
consider in what follows.
% Added in response to Reviewer 2
\cite{Cramer:2021} investigates the performance of submitted forecasts for
state-level deaths and shows that time series models perform among the top 5.
In the Supplement, we compare the time series models investigated in this paper
to the submitted case forecasts over the same period. The comparison is not
particularly flattering: the simple models examined here outperform most
submitted models and approach the accuracy of the COVIDHub Ensemble used by the
CDC.

@@

Finally, it is worth noting that examining the importance of additional features
for prediction is a core question in inferential statistics and econometrics,
with work dating back to at least \cite{Granger:1969}. Still today, drawing
rigorous inference based on predictions, without (or with lean) assumptions, is
an active field of research from both the applied and theoretical angles;
see, e.g., \cite{Diebold:2002, McCraken:2007, Diebold:2015, Stokes:2017,
  Lei:2018, Rinaldo:2019, Williamsom:2020, Zhang:2020, Dai:2021, Fryer:2021}.
Our take on this problem is in line with much of this literature; however, in
order to avoid making any explicit assumptions, we do not attempt to make formal 
significance statements, and instead, broadly examine the stability of our
conclusions with respect to numerous modes of analysis.
% Addition upon review
In the Supplement we examine
two assumption-lean
methods for assessing the statistical significance of our main results.

### 2021-09-30 forecast/paper/supplement-text.tex
modifications after the first revision meeting.

>>>>

\section{Comparisons to state-of-the-art forecasters}

Since mid-July 2020, a number of forecasting teams (48 in total) have submitted
1--4 week ahead state-level case forecasts to the COVID19 Forecast Hub
\cite{ForecastHub}. To compare those forecasts to those created in this paper,
we selected only those forecasters who submitted at least 300 forecasts for the
2-week-ahead target before
January 1, 2021 (approximately 1 forecast for each state for 6 weeks). This left
32 forecasters, one of which, the COVIDhub-4-week-ensemble, was an exact
duplicate of another. To make the comparison fair, we scaled by the
COVIDhub-baseline as in Figure 3 of the manuscript. Figure
\ref{fig:compare-to-hub-mean} shows all submitted forecasts (available 7, 14,
and 21 days ahead) overlaid on Figure 3. We have highlighted the
COVIDhub-ensemble in light blue for comparison. All the models developed in this
paper beat the baseline, and would rank in the top 8 of 31 submitted forecasts
over this period.

A more fair comparison that directly adjusts for spatiotemporal difficulty is to
use the geometric mean scaled by the baseline. This is the same idea shown in
\ref{fig:fcast-adjusted}. We have also remade this figure overlaying submitted
forecasts available on the Forecast Hub. It occasionally happens that a
submitted forecast achieved a WIS of 0, so in this case we use the WIS$+ 1$
rather than WIS for all forecasters. The result is shown in
\ref{fig:compare-to-hub-geomean}. By this metric, the methods employed in this
paper would rank in the top 2, beating the COVIDhub-ensemble at all forecast
horizons. The improvement of the best indicator assisted model over the AR model
is roughly the same as the improvement of the AR model over the COVIDhub-ensemble.
